---
title: "p8105_hw1_xm2229_050120"
author: "Xiaoyue Ma"
date: "5/1/2020"
output: html_document
---

Problem 1

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame comprised of:

a random sample of size 8 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 8
a factor vector of length 8, with 3 different factor “levels”
Try to take the mean of each variable in your dataframe. What works and what doesn’t?

In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

In a second code chunk:

convert the logical vector to numeric, and multiply the random sample by the result
convert the logical vector to a factor, and multiply the random sample by the result
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
library(tidyverse)

problem_1_df = tibble(
  random_sample = rnorm(8),
  Logical_vec = random_sample > 0,
  character_vec = length(8),
  factor_vec = c(factor("red", "blue", "white"))
)

mean_rand_samp = mean(pull(problem_1_df, random_sample))
mean_log_vec = mean(pull(problem_1_df, Logical_vec))
mean_cha_vec = mean(pull(problem_1_df, character_vec))
mean_fac_vec = mean(pull(problem_1_df, factor_vec))
```
*  Mean of the random sample in `problem_1_df` is `r mean_rand_samp`
*  Mean of the logical vector in `problem_1_df` is `r mean_log_vec`
*  Mean of the character vector in `problem_1_df` is `r mean_cha_vec`
*  Mean of the factor vector in `problem_1_df` does not exist


```{r}
numr_log = as.numeric(pull(problem_1_df, Logical_vec))
numr_char = as.numeric(pull(problem_1_df, character_vec))
numr_fac = as.numeric(pull(problem_1_df, factor_vec))

multiple_logical_numeric = numr_log * pull(problem_1_df, random_sample)
multiple_logical_factor = as.factor(pull(problem_1_df, Logical_vec)) * pull(problem_1_df, random_sample)
multiple_logical_factor_numeric = as.numeric(as.factor(pull(problem_1_df, Logical_vec)))* pull(problem_1_df, random_sample)


```
After applying the `as.numeric`, only the factor variable has an result of N/A which is in line with the result of mean. 












